Extreme heterogeneity of influenza virus infection in single cells

### 2017-09-26 paper/paper.tex
give manually edited figures separate names

\begin{figure}
\centerline{\includegraphics[width=0.9\linewidth]{figures/p_flu_expr.pdf}}
\caption{\label{fig:fluexpr}
Relative expression of influenza virus genes in highly infected cells (>5\% of total mRNA from virus).
{\bf (A)} 
The fraction of viral mRNA from each viral gene for each cell. 
{\bf (B)}
Box plots showing the distribution of the fraction of viral mRNA per cell from each viral gene.
The black lines at the notches are the medians, and the tops and bottoms of boxes indicate the first and third quartiles.
Whiskers extend to the highest or lowest data point observed within 1.5x the interquartile range, outliers shown as circles.
Notches extend 1.58x the interquartile range divided by the square root of the number of observations. 
{\bf (C)}, {\bf (D)} 
The same plots, but only including cells for which we observed at least one molecule of each viral gene.
}
\figdata{The raw data are in \texttt{p\_flu\_expr.csv}.}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=0.9\linewidth]{figures/p_small_tsne_merge.pdf}}
\caption{\label{fig:tsne}
A t-SNE plot created by semi-supervised clustering using genes that co-vary with viral infection status.
Each point is a single cell, and each panel shows an identical layout but colors the cells according to a different property.
{\bf (A), (B)}
Cells colored by the fraction of their mRNA derived from virus.
{\bf (C)}
Cells colored by the experimental sample.
{\bf (D), (E)}
Cells colored by the number of detected transcripts from type I and III interferons (IFN).
Only one cell has detectable interferon expression (in red near the lower left of the plot).
{\bf (E)}
Cells colored by the expression of the interferon-stimulated gene IFIT1.
{\bf (F)}
Cells colored by whether they express the viral NS gene.
The one interferon-positive cell is lacking NS, but so are many interferon-negative cells.
}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=0.7\linewidth]{figures/p_cellular_heatmap.pdf}}
\caption{\label{fig:cellulargenes}
Cellular genes that co-vary in expression with the amount of viral mRNA in cells expressing all eight viral genes.
The columns are cells, ordered from left to right by the fraction of mRNA derived from virus.
Each row is a gene that is differentially expressed as a function of the fraction of mRNA derived from virus at a false discovery rate of 0.1. 
Genes for which the color goes from blue at left to red at right are expressed at higher levels in cells with more viral mRNA.
The scale bar indicates the number of standard deviations above or below the mean expression, truncated at 3-fold on both sides. 
}
\figdata{The full results of the differential expression test is in \texttt{p\_sig\_cellular\_genes.csv}.}
\figdata{The results of a gene-set analysis are in \texttt{p\_sig\_cellular\_genes.csv}.}
\figsupp[Many genes that co-vary with viral load are involved in the oxidative stress response. \label{figsupp:ROStable}]{
Table delineating genes in Figure~\ref{fig:cellulargenes} that are associated with the response to oxidative stress~\citep{Duong:2017ju,Jung:2017jz,Lee:2017ba,Peuchant:2017hj,MacLeod:2016kt,Jiang:2016cf,Gorrini:2013jv,Miura:2013fr,Kim:2009gi,Banning:2005cz,Murray:2003ie,Doyle:1999ts}.
}{\includegraphics[width=0.7\linewidth]{figures/ROStable.pdf}}
\end{figure}

>>>>

\begin{figure}
\centerline{\includegraphics[width=0.9\linewidth]{figures/p_flu_expr_manualedits.pdf}}
\caption{\label{fig:fluexpr}
Relative expression of influenza virus genes in highly infected cells (>5\% of total mRNA from virus).
{\bf (A)} 
The fraction of viral mRNA from each viral gene for each cell. 
{\bf (B)}
Box plots showing the distribution of the fraction of viral mRNA per cell from each viral gene.
The black lines at the notches are the medians, and the tops and bottoms of boxes indicate the first and third quartiles.
Whiskers extend to the highest or lowest data point observed within 1.5x the interquartile range, outliers shown as circles.
Notches extend 1.58x the interquartile range divided by the square root of the number of observations. 
{\bf (C)}, {\bf (D)} 
The same plots, but only including cells for which we observed at least one molecule of each viral gene.
}
\figdata{The raw data are in \texttt{p\_flu\_expr.csv}.}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=0.9\linewidth]{figures/p_small_tsne_merge_manualarrow.pdf}}
\caption{\label{fig:tsne}
A t-SNE plot created by semi-supervised clustering using genes that co-vary with viral infection status.
Each point is a single cell, and each panel shows an identical layout but colors the cells according to a different property.
{\bf (A), (B)}
Cells colored by the fraction of their mRNA derived from virus.
{\bf (C)}
Cells colored by the experimental sample.
{\bf (D), (E)}
Cells colored by the number of detected transcripts from type I and III interferons (IFN).
Only one cell has detectable interferon expression (in orange, indicated with arrow).
{\bf (E)}
Cells colored by the expression of the interferon-stimulated gene IFIT1.
{\bf (F)}
Cells colored by whether they express the viral NS gene.
The one interferon-positive cell is lacking NS, but so are many interferon-negative cells.
}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=0.7\linewidth]{figures/p_cellular_heatmap_manualedit.pdf}}
\caption{\label{fig:cellulargenes}
Cellular genes that co-vary in expression with the amount of viral mRNA in cells expressing all eight viral genes.
The columns are cells, ordered from left to right by the fraction of mRNA derived from virus.
Each row is a gene that is differentially expressed as a function of the fraction of mRNA derived from virus at a false discovery rate of 0.1. 
Genes for which the color goes from blue at left to red at right are expressed at higher levels in cells with more viral mRNA.
The scale bar indicates the number of standard deviations above or below the mean expression, truncated at 3-fold on both sides. 
}
\figdata{The full results of the differential expression test is in \texttt{p\_sig\_cellular\_genes.csv}.}
\figdata{The results of a gene-set analysis are in \texttt{p\_sig\_cellular\_genes.csv}.}
\figsupp[Many genes that co-vary with viral load are involved in the oxidative stress response. \label{figsupp:ROStable}]{
Table delineating genes in Figure~\ref{fig:cellulargenes} that are associated with the response to oxidative stress~\citep{Duong:2017ju,Jung:2017jz,Lee:2017ba,Peuchant:2017hj,MacLeod:2016kt,Jiang:2016cf,Gorrini:2013jv,Miura:2013fr,Kim:2009gi,Banning:2005cz,Murray:2003ie,Doyle:1999ts}.
}{\includegraphics[width=0.7\linewidth]{figures/ROStable.pdf}}
\end{figure}
